\chapter{Introduction}

The project chosen for this report is the creation of a web application for the Monaleen Tennis Club. This is a club within the Castletroy area, near to the University. The club uses an existing paper based system, and the goal of this report is to establish the process necessary to manage a project to provide a software solution to the organisation. 

The project group consisted of Chris O'Brien, Project Manager, with Shane Whelan and Brian O'Donoghue. We examined the process as detailed by the Project Management Body of Knowledge (PMBOK).

We focused on the following areas:

\begin{enumerate}
\item Project Integration
\item Project Scope Management
\item Project Time Management
\item Project Cost Management
\item Project Quality Management
\item Project Risk Management
\item Project Human Resource Management
\end{enumerate}

Microsoft Project, Agena Risk and Cocomo were used to manage project planning, risk, and cost. 

Our industry contract was a project manage at Fineos Software, a company that provides software for the insurance sector. They use an agile model for their development, while we choose a more traditional waterfall-based RUP (Rational Unified Process) model which was created by IBM. We discussed management practices with our contact, and made adjustments to our plans based on his advice and experience. He stressed that human resource management is an essential skill that binds the project together, and the proper allocation of these resource is essential to a projects success. They utilise daily stand up meetings to communicate progress and changes within the project. Their key focus is on the end product, what the user wants. He advised that we needed a bit more focus on requirements and software quality at an earlier stage within the project, and based on this advice we made a number of changes to expand these areas.

